Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-12 secondPaper/accordionComplexSurfaces.tex
last changes

\thanks{YP, VP and PGP were partially supported by the French ANR grant SC3A~(15\,CE40\,0004\,01).}

@@

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.6]{quivers}}
	\caption{Some locally gentle quivers (top) and their blossoming quivers (bottom). Initial vertices are solid and labeled while blossom vertices are hollow, and initial arcs are bold while blossom arcs are thin.}
	\label{fig:quivers}
\end{figure}

\begin{remark}
\label{rem:sizeBlossomingQuiver}
Note that~$\bar Q\blossom$ has~$2|Q_0|-|Q_1|$ incoming blossom arrows and~$2|Q_0|-|Q_1|$ outgoing blossom arrows.
Therefore, it has $|Q_0\blossom| = |Q_0| + 2(2|Q_0|-|Q_1|) = 5|Q_0|-2|Q_1|$ vertices and~$|Q_1\blossom| = |Q_1| + 2(2|Q_0|-|Q_1|) = 4|Q_0|-|Q_1|$ arrows.
\end{remark}

@@

@@

\begin{proof}
The duality provides a bijection~$v\in (Q_\dissection)_0\mapsto v\dual\in (Q_{\dissection\dual})_0$, and also induces a bijection~${\alpha \in (Q_\dissection)_1 \mapsto \alpha\dual \in (Q_{\dissection\dual})_1}$ with~$s(\alpha\dual) = t(\alpha)\dual$ and~$t(\alpha\dual) = s(\alpha)\dual$.
 Moreover, for any two composable arrows~$\alpha,\beta\in(Q_\dissection)_0$, we have~$\alpha\beta\in I_\dissection$ if and only if~$s(\alpha),t(\alpha),t(\beta)$ are three consecutive edges of a~$\dissection$-cell~$f$, if and only if~$s(\alpha)\dual,t(\alpha)\dual,t(\beta)\dual$ are three consecutive arcs in~$\dissection\dual$ ending in~$f\dual$, if and only if~$\beta\dual\alpha\dual\notin I_{\dissection\dual}$.
\end{proof}

@@

\begin{remark}
\label{rem:propertiesSurface}
The following observations are useful for the computation of examples.
\begin{enumerate}[(i)]
\item The set~$V_{\bar Q}$ has one vertex for each straight walk in~$\bar Q$ (equivalently, for each maximal path in~$\bar Q$).
      Finite straight walks yield vertices on the boundary of~$\surface_{\bar Q}$, while infinite cyclic straight walks in~$\bar Q$ yield punctures~$\surface_{\bar Q}$ in~$V_{\bar Q}$.
      We denote by~$p$ the number of infinite cyclic straight walks in~$\bar Q$.
\item \label{item:arcs}
      The dissection~$\dissection_{\bar Q}$ has one edge for each vertex~$v \in \bar Q_0$, obtained by concatenation of the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$v = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$. We denote by~$\edgeof(v)$ the edge of~$\dissection_{\bar Q}$ corresponding to~$v$.
\item The dissection~$\dissection_{\bar Q}$ has one $\ell$-cell for each straight walk of length~$\ell$ in~$\bar Q\koszul$.
\item Similar statements hold dually for~${{V\dual}\!\!_{\bar Q}}$ and~${\dissection\dual\!\!_{\bar Q}}$, and the notations~$p\dual$ and~$\dualedgeof(v)$ are defined similarly.
\item The number of punctures of~$\surface_{\bar Q}$ is the number~$p + p\dual$ of infinite straight walks in~$\bar Q$ and in~$\bar Q\koszul$.
\item \label{item:boundary}
      The number~$b$ of boundary components of~$\surface_{\bar Q}$ can be computed as follows.
      There are two natural perfect matchings whose vertices are the blossom vertices of~$\bar Q$: one is obtained by joining the endpoints of each finite straight walk of~$\bar Q$, and the other is obtained similarly from~$\bar Q \koszul$.
      Let~$G$ be the superposition of these two perfect matchings.
      Then the number~$b$ of boundary components of~$\surface_{\bar Q}$ is the number of connected components of~$G$.
\item The genus of the surface~$\surface_{\bar Q}$ is
      \[
       g = \frac{|Q_1| - |Q_0| - b - p - p\dual + 2}{2},
      \]
      where~$b$ is the number of boundary components (see above for a way to compute~$b$) and~$p$ the number of punctures (\ie infinite straight walks in~$\bar Q$ and in~$\bar Q\koszul$).
      Indeed, ${2g = 2-\chi(\surface_{\bar Q})}$, where~$\chi(\surface_{\bar Q})$ is the Euler characteristic of~$\surface_{\bar Q}$.
      The dissection~$\dissection$ provides a cellular decomposition of~$\surface_{\bar Q}$ on which we fill the boundary components with disks.  
      The number of faces of this cellular decomposition is~$b + p\dual$, its number of edges is~$|Q_0|$ and its number of vertices is the number of straight walks in~$\bar Q$, which is equal to~$2|Q_0| - |Q_1| + p$.
      The above formula for~$g$ follows.
\end{enumerate}
\end{remark}

@@

We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,(\ref{item:boundary})) form a cycle with green and red arrows alternating.
Moreover, $\bar Q$ and~$\bar Q\koszul$ have no infinite straight walks.
Since~$|Q_1| = |Q_0|-1$, the corresponding surfaces are disks ($1$ boundary component, no puncture and genus~$0$).
Two examples are represented in \fref{fig:reversedPathsSurfaces}.
Note that the dissection~$\dissection_{\bar Q}$ is a triangulation with no internal triangles, and the orientation of~$\bar Q$ indicates how to glue these triangles.
For instance, the Cambrian quiver completely oriented in one direction yields a fan triangulation, were all internal arcs are incident to the same vertex, as in \fref{fig:CambrianPathsSurfaces}\,(left).

@@

We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,(\ref{item:boundary})) look like~\raisebox{-.1cm}{\includegraphics[scale=.3]{reversedPathsPM}}.
Moreover, $\bar Q$ has no infinite straight walk, while~$\bar Q\koszul$ has~$|Q_0|-1$ infinite straight walks.
Since~$|Q_1| = 2|Q_0|-2$, the corresponding surfaces have $1$ boundary component and genus~$0$.
The first few corresponding surfaces are represented in \fref{fig:reversedPathsSurfaces}.

@@

\enlargethispage{.2cm}
We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,(\ref{item:boundary})) look like~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPModd}} when~$|Q_0|$ is odd and~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPMeven}} when~$|Q_0|$ is even.
Moreover, $\bar Q$ and~$\bar Q\koszul$ have no infinite straight walks.
Since~$|Q_1| = 2|Q_0|-2$, the corresponding surfaces have no punctures and
\begin{itemize}
\item $1$ boundary component and genus~$(|Q_0|-1)/2$ when~$|Q_0|$ is odd, and 
\item $2$ boundary components and genus~$(|Q_0|-2)/2$ when~$|Q_0|$ is even.
\end{itemize}
The first few corresponding surfaces are represented in \fref{fig:doublePathsSurfaces}.

@@

We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,(\ref{item:boundary})) form a cycle with green and red arrows alternating.
Moreover, $\bar Q$ has~$1$ infinite straight walk, while~$\bar Q\koszul$ has none.
Since~$|Q_1| = |Q_0|$, the corresponding surfaces are punctured disks ($1$ boundary component, $1$ puncture and genus~$0$).
The first few corresponding surfaces are represented in \fref{fig:cyclesSurfacesBis} (see Figures~\ref{fig:surfaces} and~\ref{fig:reversedPathsSurfaces} for the cycles with $1$ or~$2$ vertices, recalling that~$\bar Q$ and~$\bar Q\koszul$ yield the same surface).

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.7]{cyclesSurfacesBis}}
	\caption{The surface~$\surface_{\bar Q}$ for the cycle quivers with~$3, 4, 5$ vertices.}
	\label{fig:cyclesSurfacesBis}
\end{figure}
\end{example}

@@

We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,(\ref{item:boundary})) are empty since there is no blossom vertices.
Moreover, $\bar Q$ has~$1$ infinite straight walk when~$|Q_0|$ is odd and~$2$ when~$|Q_0|$ is even, and~$\bar Q\koszul$ always has~$2$ infinite straight walks.
Since~$|Q_1| = 2|Q_0|$, the corresponding surfaces have no boundary component and
\begin{itemize}
\item $3$ punctures and genus~$(|Q_0|-1)/2$ when~$|Q_0|$ is odd, and 
\item $4$ punctures and genus~$(|Q_0|-2)/2$ when~$|Q_0|$ is even.
\end{itemize}
The first few corresponding surfaces are represented in \fref{fig:doubleCyclesSurfaces}.

@@

Let~$\bar Q$ be a locally gentle bound quiver.
For each arc of the dissection~$\dissection_{\bar Q}$ on~$\surface_{\bar Q}$, we fix a point on the interior of this arc, which we call its ``middle point'' (this is the black vertex on the pictures).
To each walk on~$\bar Q$, we will now associate a~$\dissection_{\bar Q}$-accordion.

\begin{definition}
\label{def:curveOfAnArrow}
For any arrow~$\alpha$ on $\bar Q\blossom$, let~$\curveof(\alpha)$ be the curve on~$\surface_{\bar Q}$ which goes from the middle point of the arc corresponding to $s(\alpha)$ to the middle point of the arc corresponding to $t(\alpha)$ by following the angle corresponding to~$\alpha$.
Define~$\curveof(\alpha^{-1})$ to be~$\curveof(\alpha)^{-1}$.
\end{definition}

@@

\begin{proof}
We can assume that~$\gamma$ intersects itself and the arcs of~$\dissection_{\bar Q}$ transversaly and minimally, in the sense that~$\gamma$ does not cross an arc twice in succession in opposite directions (see Definition~\ref{def:crossingCurves}).
Then~$\gamma$ is completely determined by its sequence of intersection points with the arcs of~$\dissection_{\bar Q}$, since the dissection is cellular.
Two successive intersection points in this sequence define an angle between two arcs of~$\dissection_{\bar Q}$, which corresponds to an arrow in~$\bar Q$.
Thus the sequence of intersection points defines a walk~$\walk(\gamma)$ on~$\bar Q$.
By construction, we have that~$\curveof(\walk(\gamma)) = \gamma$.
Is also follows from the construction above and from Definition~\ref{def:curveOfAWalk} that~$\walk(\curveof(\omega)) = \omega$ for any walk~$\omega$.
This finishes the proof.
\end{proof}

@@

\begin{lemma}
\label{lem:nonKissing=nonCrossing}
Let~$\omega_1$ and~$\omega_2$ be walks on~$\bar Q$.  Then~$\omega_1$ and~$\omega_2$ are non-kissing if and only if the~$\dissection_{\bar Q}$-accordions~$\curveof(\omega_1)$ and~$\curveof(\omega_2)$ are non-crossing on~$\surface_{\bar Q}$.
\end{lemma}

@@

\begin{remark}
Note that our construction of the surface~$\surface_{\bar Q}$ implies that the vertices of~$\bar Q$ are naturally identified with the intersection points of the dual edges~$a \in \dissection_{\bar Q}$ and~$a\dual \in {\dissection\dual\!\!_{\bar Q}}$.
If we force all $\dissection$-accordions (or $\dissection\dual$-slaloms) to cross the edges of~$\dissection$ and~$\dissection\dual$ only at these intersection points, then a $\dissection$-accordion (or $\dissection\dual$-slalom) is really seen as a walk on~$\bar Q$.
\end{remark}

@@

\begin{example}
\label{exm:peakDeepFacets}
We have seen in Definition~\ref{def:straightBending} that each vertex~$v$ of~$Q$ gives rise to a \defn{peak walk}~$v_\peak$ (resp.~\defn{deep walk}~$v_\deep$) with a single peak (resp.~deep) at~$v$ and no other corner.
The set of all such walks forms the \defn{peak facet}~$\set{v_\peak}{v \in Q_0}$ (resp.~the \defn{deep facet}~$\set{v_\deep}{v \in Q_0}$) of the non-kissing complex~$\RNKC$.
As an example of Theorem~\ref{thm:complexesCoincide}, let us now describe the corresponding non-crossing facets of~$\RNCC[\surface_{\bar Q}]$.

@@

We invite the reader to check that~$\curveof(v_\peak) = \vprevious{\edgeof(v)}$ (resp.~$\curveof(v_\deep) = \vnext{\edgeof(v)}$), where~$\edgeof(v)$ denotes the edge of~$\dissection$ corresponding to~$v \in Q_0$ (see Remark~\ref{rem:propertiesSurface}).
Therefore, the peak facet (resp.~the deep facet) can be thought of as the dissection~$\dissection$ slightly rotated clockwise (resp.~counterclockwise) on the surface~$\surface$.
\end{example}

@@

\begin{remark}
\label{rem:countercurrentOrderOnSurface}
Using Theorem \ref{thm:complexesCoincide}, we can translate the definition of the countercurrent order~$\prec_\alpha$ to the language of~$\dissection$-accordions (resp.~of~$\dissection\dual$-slaloms).
An arrow~$\alpha$ in~$\bar Q\blossom$ corresponds to an angle at a point~$v$ between two arcs of~$\dissection$ (resp.~at a point~$v\dual$ between two arcs of~$\dissection\dual$).
Two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at~$\alpha$ in~$\bar Q$ correspond to two distinct non-crossing~$\dissection$-accordions (resp.~$\dissection\dual$-slaloms)~$\gamma$ and~$\delta$ passing in front of this angle.
Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer to~$v$ (resp.~further to~$v\dual$) than~$\delta$ does.
These interpretations of~$\prec_\alpha$ on the surface where already considered in the case of the disk in~\cite{GarverMcConville, MannevillePilaud-accordion}.
%
\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=1]{orderCurves}}
	\caption{The order~$\mu \prec_\alpha \nu$ on marked walks is the order in which the corresponding curves~$\curveof(\mu)$ and~$\curveof(\nu)$ cross the angles of~$\dissection$ and~$\dissection\dual$ corresponding to~$\alpha$.}
	\label{fig:orderCurves}
\end{figure}
\end{remark}

@@

 \para{Geometric proof}
 View~$F$ as a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$.
 The arrow~$\alpha$ then corresponds to an angle in~$\dissection$ at a vertex~$v$.

 For any curve~$\gamma$ in~$F$, even though~$\gamma$ may pass through the above angle infinitely many times, there is one instance that is furthest from the angle:
 indeed, if ~$\gamma$ passes infinitely many times through~$\alpha$, then~$v$ is a puncture and~$\gamma$ circles infinitely towards it.
 But then~$\gamma$ passes through~$\alpha$ only finitely many times before it starts circling~$v$ (in either direction), and one of these times is the furthest from~$v$.

 Therefore, for every curve~$\gamma\in F$, there is a maximal occurence of~$\alpha$ in~$\gamma$.
 Since~$F$ is finite, the set of these maximal occurences is finite, so it admits a maximal element.  
 This element is the maximal element of~$F_\alpha$.
\end{proof}

@@

\begin{definition}
\label{defi:distinguishedWalksAndArrows}
Let~$\alpha \in Q\blossom_1$ be an arrow and let~$F$ be a face of~$\NKC$ containing the straight walk passing through~$\alpha$.
Consider the marked walk~$\omega_\star \eqdef \max_{\prec_\alpha} F_\alpha$ (which exists by Lemma~\ref{lemm:facesHaveMaximalElement} and Proposition~\ref{prop:facetsAreFinite}),
and let~$\omega$ be the walk obtained by forgetting the marked arrow in~$\omega_\star$. 
We say that~$\omega$ is the \defn{distinguished walk} of~$F$ at~$\alpha$ and that~$\alpha$ is a \defn{distinguished arrow} on~$\omega \in F$.
We will use the notation
\[
\distinguishedWalk{\alpha}{F} \eqdef \max\nolimits_{\prec_\alpha} F_\alpha
\qquad\text{and}\qquad
\distinguishedArrows{\omega}{F} \eqdef \set{\alpha \in \omega}{\distinguishedWalk{\alpha}{F} = \omega}.
\]
\end{definition}

@@

Let~$\bar Q = (Q,I)$ be a locally gentle bound quiver, and let~$(\b{e}_v)_{v \in Q_0}$ be the standard basis of~$\R^{Q_0}$.

>>>>

\thanks{YP, VP and PGP were partially supported by the French ANR grant SC3A~(15\,CE40\,0004\,01). VP was partially supported by the French ANR grant CAPPS~(17\,CE40\,0018).}

@@

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.6]{quivers}}
	\caption{Some locally gentle quivers (top) and their blossoming quivers (bottom). Initial vertices are solid and labeled while blossom vertices are hollow, and initial arrows are bold while blossom arrows are thin.}
	\label{fig:quivers}
\end{figure}

\begin{remark}
\label{rem:sizeBlossomingQuiver}
Note that~$\bar Q\blossom$ has~$2|Q_0|-|Q_1|$ incoming blossom arrows and~$2|Q_0|-|Q_1|$ outgoing blossom arrows.
Therefore, it has $|Q_0\blossom| = |Q_0| + 2(2|Q_0|-|Q_1|) = 5|Q_0|-2|Q_1|$ vertices and~${|Q_1\blossom| = |Q_1| + 2(2|Q_0|-|Q_1|) = 4|Q_0|-|Q_1|}$ arrows.
\end{remark}

@@

For any arrow~$\alpha$ of~$Q$, define a formal inverse~$\alpha^{-1}$ with the properties that~${s(\alpha^{-1}) = t(\alpha)}$, $t(\alpha^{-1}) = s(\alpha)$, $\alpha^{-1}\alpha = \varepsilon_{t(\alpha)}$ and~$\alpha\alpha^{-1} = \varepsilon_{s(\alpha)}$, where~$\varepsilon_v$ is the path of length zero starting and ending at the vertex~$v \in Q_0$. % Furthermore, let~$(\alpha^{-1})^{-1}=\alpha$; thus~$(-)^{-1}$ is an involution on the set of arrows and formal inverses of arrows of~$Q$.  We extend this involution to the set of all paths involving arrows or their formal inverses by further setting~$(\varepsilon_v)^{-1} = \varepsilon_v$ for all vertices~$v \in Q_0$.

@@

\begin{proof}
The duality provides a bijection~$v\in (Q_\dissection)_0\mapsto v\dual\in (Q_{\dissection\dual})_0$, and also induces a bijection~${\alpha \in (Q_\dissection)_1 \mapsto \alpha\dual \in (Q_{\dissection\dual})_1}$ with~$s(\alpha\dual) = t(\alpha)\dual$ and~$t(\alpha\dual) = s(\alpha)\dual$.
 Moreover, for any two composable arrows~$\alpha,\beta\in(Q_\dissection)_0$, we have~$\alpha\beta\in I_\dissection$ if and only if~$s(\alpha),t(\alpha),t(\beta)$ are three consecutive edges of a~$\dissection$-cell~$f$, if and only if~$s(\alpha)\dual,t(\alpha)\dual,t(\beta)\dual$ are three consecutive edges in~$\dissection\dual$ ending in~$f\dual$, if and only if~$\beta\dual\alpha\dual\notin I_{\dissection\dual}$.
\end{proof}

@@

\begin{remark}
\label{rem:propertiesSurface}
The following observations are useful for the computation of examples.
\begin{enumerate}[(i)]
\item The set~$V_{\bar Q}$ has one vertex for each straight walk in~$\bar Q$ (equivalently, for each maximal path in~$\bar Q$).
      Finite straight walks yield vertices on the boundary of~$\surface_{\bar Q}$, while infinite cyclic straight walks in~$\bar Q$ yield punctures~$\surface_{\bar Q}$ in~$V_{\bar Q}$.
      We denote by~$p$ the number of infinite cyclic straight walks in~$\bar Q$.
\item \label{item:edges}
      The dissection~$\dissection_{\bar Q}$ has one edge for each vertex~$v \in \bar Q_0$, obtained by concatenation of the sides~$\Enrt{\alpha} = \Enrs{\beta}$ and~$\Enrt{\alpha'} = \Enrs{\beta'}$ where~$v = t(\alpha) = s(\beta) = t(\alpha') = s(\beta')$, $\alpha\beta \notin I$ and~$\alpha'\beta' \notin I$. We denote by~$\edgeof(v)$ the edge of~$\dissection_{\bar Q}$ corresponding to~$v$.
\item The dissection~$\dissection_{\bar Q}$ has one $\ell$-cell for each straight walk of length~$\ell$ in~$\bar Q\koszul$.
\item Similar statements hold dually for~${{V\dual}\!\!_{\bar Q}}$ and~${\dissection\dual\!\!_{\bar Q}}$, and the notations~$p\dual$ and~$\dualedgeof(v)$ are defined similarly.
\item The number of punctures of~$\surface_{\bar Q}$ is the number~$p + p\dual$ of infinite straight walks in~$\bar Q$ and in~$\bar Q\koszul$.
\item \label{item:boundary}
      The number~$b$ of boundary components of~$\surface_{\bar Q}$ can be computed as follows.
      There are two natural perfect matchings whose vertices are the blossom vertices of~$\bar Q$: one is obtained by joining the endpoints of each finite straight walk of~$\bar Q$, and the other is obtained similarly from~$\bar Q \koszul$.
      Let~$G$ be the superposition of these two perfect matchings.
      Then the number~$b$ of boundary components of~$\surface_{\bar Q}$ is the number of connected components of~$G$.
\item The genus of the surface~$\surface_{\bar Q}$ is
      \[
       g = \frac{|Q_1| - |Q_0| - b - p - p\dual + 2}{2},
      \]
      where~$b$ is the number of boundary components (see above for a way to compute~$b$) and~$p$ the number of punctures (\ie infinite straight walks in~$\bar Q$ and in~$\bar Q\koszul$).
      Indeed, ${2g = 2-\chi(\surface_{\bar Q})}$, where~$\chi(\surface_{\bar Q})$ is the Euler characteristic of~$\surface_{\bar Q}$.
      The dissection~$\dissection$ provides a cellular decomposition of~$\surface_{\bar Q}$ on which we fill the boundary components with disks.  
      The number of faces of this cellular decomposition is~$b + p\dual$, its number of edges is~$|Q_0|$ and its number of vertices is the number of straight walks in~$\bar Q$, which is equal to~$2|Q_0| - |Q_1| + p$.
      The above formula for~$g$ follows.
\end{enumerate}
\end{remark}

@@

We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,\eqref{item:boundary}) form a cycle with green and red arrows alternating.
Moreover, $\bar Q$ and~$\bar Q\koszul$ have no infinite straight walks.
Since~$|Q_1| = |Q_0|-1$, the corresponding surfaces are disks ($1$ boundary component, no puncture and genus~$0$).
Two examples are represented in \fref{fig:reversedPathsSurfaces}.
Note that the dissection~$\dissection_{\bar Q}$ is a triangulation with no internal triangles, and the orientation of~$\bar Q$ indicates how to glue these triangles.
For instance, the Cambrian quiver completely oriented in one direction yields a fan triangulation, were all internal arcs are incident to the same vertex, as in \fref{fig:CambrianPathsSurfaces}\,(left).

@@

We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,\eqref{item:boundary}) look like~\raisebox{-.1cm}{\includegraphics[scale=.3]{reversedPathsPM}}.
Moreover, $\bar Q$ has no infinite straight walk, while~$\bar Q\koszul$ has~$|Q_0|-1$ infinite straight walks.
Since~$|Q_1| = 2|Q_0|-2$, the corresponding surfaces have $1$ boundary component and genus~$0$.
The first few corresponding surfaces are represented in \fref{fig:reversedPathsSurfaces}.

@@

\enlargethispage{.2cm}
We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,\eqref{item:boundary}) look like~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPModd}} when~$|Q_0|$ is odd and~\raisebox{-.1cm}{\includegraphics[scale=.3]{doublePathsPMeven}} when~$|Q_0|$ is even.
Moreover, $\bar Q$ and~$\bar Q\koszul$ have no infinite straight walks.
Since~$|Q_1| = 2|Q_0|-2$, the corresponding surfaces have no punctures and
\begin{itemize}
\item $1$ boundary component and genus~$(|Q_0|-1)/2$ when~$|Q_0|$ is odd, and 
\item $2$ boundary components and genus~$(|Q_0|-2)/2$ when~$|Q_0|$ is even.
\end{itemize}
The first few corresponding surfaces are represented in \fref{fig:doublePathsSurfaces}.

@@

We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,\eqref{item:boundary}) form a cycle with green and red arrows alternating.
Moreover, $\bar Q$ has~$1$ infinite straight walk, while~$\bar Q\koszul$ has none.
Since~$|Q_1| = |Q_0|$, the corresponding surfaces are punctured disks ($1$ boundary component, $1$ puncture and genus~$0$).
The first few corresponding surfaces are represented in \fref{fig:cyclesSurfaces} (see Figures~\ref{fig:surfaces} and~\ref{fig:reversedPathsSurfaces} for the cycles with $1$ or~$2$ vertices, recalling that~$\bar Q$ and~$\bar Q\koszul$ yield the same surface).

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.7]{cyclesSurfacesBis}}
	\caption{The surface~$\surface_{\bar Q}$ for the cycle quivers with~$3, 4, 5$ vertices.}
	\label{fig:cyclesSurfaces}
\end{figure}
\end{example}

@@

We apply Remark~\ref{rem:propertiesSurface} to understand the corresponding surfaces.
The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}\,\eqref{item:boundary}) are empty since there are no blossom vertices.
Moreover, $\bar Q$ has~$1$ infinite straight walk when~$|Q_0|$ is odd and~$2$ when~$|Q_0|$ is even, and~$\bar Q\koszul$ always has~$2$ infinite straight walks.
Since~$|Q_1| = 2|Q_0|$, the corresponding surfaces have no boundary component and
\begin{itemize}
\item $3$ punctures and genus~$(|Q_0|-1)/2$ when~$|Q_0|$ is odd, and 
\item $4$ punctures and genus~$(|Q_0|-2)/2$ when~$|Q_0|$ is even.
\end{itemize}
The first few corresponding surfaces are represented in \fref{fig:doubleCyclesSurfaces}.

@@

Let~$\bar Q$ be a locally gentle bound quiver.
For each edge of the dissection~$\dissection_{\bar Q}$ on~$\surface_{\bar Q}$, we fix a point on the interior of this edge, which we call its ``middle point'' (this is the black vertex on the pictures).
To each walk on~$\bar Q$, we will now associate a~$\dissection_{\bar Q}$-accordion.

\begin{definition}
\label{def:curveOfAnArrow}
For any arrow~$\alpha$ on $\bar Q\blossom$, let~$\curveof(\alpha)$ be the curve on~$\surface_{\bar Q}$ which goes from the middle point of the edge of~$\dissection$ corresponding to $s(\alpha)$ to the middle point of the edge of~$\dissection$ corresponding to $t(\alpha)$ by following the angle corresponding to~$\alpha$.
Define~$\curveof(\alpha^{-1})$ to be~$\curveof(\alpha)^{-1}$.
\end{definition}

@@

\begin{proof}
We can assume that~$\gamma$ intersects itself and the edges of~$\dissection_{\bar Q}$ transversaly and minimally, in the sense that~$\gamma$ does not cross an edge twice in succession in opposite directions (see Definition~\ref{def:crossingCurves}).
Then~$\gamma$ is completely determined by its sequence of intersection points with the edges of~$\dissection_{\bar Q}$, since the dissection is cellular.
Two successive intersection points in this sequence define an angle between two edges of~$\dissection_{\bar Q}$, which corresponds to an arrow in~$\bar Q$.
Thus the sequence of intersection points defines a walk~$\walk(\gamma)$ on~$\bar Q$.
By construction, we have that~$\curveof(\walk(\gamma)) = \gamma$.
Is also follows from the construction above and from Definition~\ref{def:curveOfAWalk} that~$\walk(\curveof(\omega)) = \omega$ for any walk~$\omega$.
This finishes the proof.
\end{proof}

@@

\begin{lemma}
\label{lem:nonKissing=nonCrossing}
Two undirected walks~$\omega_1$ and~$\omega_2$ on~$\bar Q$ are non-kissing if and only if the corresponding $\dissection_{\bar Q}$-accordions~$\curveof(\omega_1)$ and~$\curveof(\omega_2)$ are non-crossing on~$\surface_{\bar Q}$.
\end{lemma}

@@

\begin{remark}
Note that our construction of the surface~$\surface_{\bar Q}$ implies that the quiver~$\bar Q$ is naturally embedded on~$\surface_{\bar Q}$.
If we force all $\dissection$-accordions (or $\dissection\dual$-slaloms) to follow the arrows of~$\bar Q$, then a $\dissection$-accordion (or $\dissection\dual$-slalom) is really seen as a walk on~$\bar Q$.
\end{remark}

@@

\begin{example}
\label{exm:peakDeepFacets}
We have seen in Definition~\ref{def:straightBending} that each vertex~$v$ of~$Q$ gives rise to a \defn{peak walk}~$v_\peak$ (resp.~\defn{deep walk}~$v_\deep$) with a single peak (resp.~deep) at~$v$ and no other corner.
The set of all such walks forms the \defn{peak facet}~$\set{v_\peak}{v \in Q_0}$ (resp.~the \defn{deep facet}~$\set{v_\deep}{v \in Q_0}$) of the non-kissing complex~$\RNKC$.
As an example of Theorem~\ref{thm:complexesCoincide}, let us now describe the corresponding non-crossing facets of~$\RNCC[\dissection_{\bar Q}, {{\dissection\dual}\!\!_{\bar Q}}]$.

@@

We invite the reader to check that~$\curveof(v_\peak) = \vprevious{\edgeof(v)}$ (resp.~$\curveof(v_\deep) = \vnext{\edgeof(v)}$), where~$\edgeof(v)$ denotes the edge of~$\dissection_{\bar Q}$ corresponding to~$v \in Q_0$ (see Remark~\ref{rem:propertiesSurface}\,\eqref{item:edges}).
Therefore, the peak facet (resp.~the deep facet) can be thought of as the dissection~$\dissection_{\bar Q}$ slightly rotated clockwise (resp.~counterclockwise) on the surface~$\surface_{\bar Q}$.
\end{example}

@@

\begin{remark}
\label{rem:countercurrentOrderOnSurface}
Using Theorem \ref{thm:complexesCoincide}, we can translate the definition of the countercurrent order~$\prec_\alpha$ to the language of~$\dissection$-accordions (resp.~of~$\dissection\dual$-slaloms).
An arrow~$\alpha$ in~$\bar Q\blossom$ corresponds to an angle at a point~$v$ between two edges of~$\dissection$ (resp.~at a point~$v\dual$ between two edges of~$\dissection\dual$).
Two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at~$\alpha$ in~$\bar Q$ correspond to two distinct non-crossing~$\dissection$-accordions (resp.~$\dissection\dual$-slaloms)~$\gamma$ and~$\delta$ passing in front of this angle.
Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer to~$v$ (resp.~further to~$v\dual$) than~$\delta$ does.
These interpretations of~$\prec_\alpha$ on the surface where already considered in the case of the disk in~\cite{GarverMcConville, MannevillePilaud-accordion}.
%
\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=1]{orderCurves}}
	\caption{The order~$\mu \prec_\alpha \nu$ on marked walks is the order in which the corresponding curves~$\curveof(\mu)$ and~$\curveof(\nu)$ cross the angles of~$\dissection$ and~$\dissection\dual$ corresponding to~$\alpha$.}
	\label{fig:orderCurves}
\end{figure}
\end{remark}

@@

\para{Geometric proof}
View~$F$ as a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection\dual\!\!_{\bar Q}}]$.
The arrow~$\alpha$ then corresponds to an angle in~$\dissection$ at a vertex~$v$.  
% 
For any curve~$\gamma$ in~$F$, even though~$\gamma$ may pass through the above angle infinitely many times, there is one instance that is furthest from the angle: indeed, if ~$\gamma$ passes infinitely many times through~$\alpha$, then~$v$ is a puncture and~$\gamma$ circles infinitely towards it.
But then~$\gamma$ passes through~$\alpha$ only finitely many times before it starts circling~$v$ (in either direction), and one of these times is the furthest from~$v$.
%  
Therefore, for every curve~$\gamma\in F$, there is a maximal occurence of~$\alpha$ in~$\gamma$.
Since~$F$ is finite, the set of these maximal occurences is finite, so it admits a maximal element.  
This element is the maximal element of~$F_\alpha$.
\end{proof}

@@

\begin{definition}
\label{def:distinguishedWalksAndArrows}
Let~$\alpha \in Q\blossom_1$ be an arrow and let~$F$ be a face of~$\NKC$ containing the straight walk passing through~$\alpha$.
Consider the marked walk~$\omega_\star \eqdef \max_{\prec_\alpha} F_\alpha$ (which exists by Lemma~\ref{lemm:facesHaveMaximalElement} and Proposition~\ref{prop:facetsAreFinite}),
and let~$\omega$ be the walk obtained by forgetting the marked arrow in~$\omega_\star$. 
We say that~$\omega$ is the \defn{distinguished walk} of~$F$ at~$\alpha$ and that~$\alpha$ is a \defn{distinguished arrow} on~$\omega \in F$.
We will use the notation
\[
\distinguishedWalk{\alpha}{F} \eqdef \max\nolimits_{\prec_\alpha} F_\alpha
\qquad\text{and}\qquad
\distinguishedArrows{\omega}{F} \eqdef \set{\alpha \in \omega}{\distinguishedWalk{\alpha}{F} = \omega}.
\]
\end{definition}

@@

Let~$\bar Q = (Q,I)$ be a locally gentle bound quiver, and let~$(\b{e}_v)_{v \in Q_0}$ denote the standard basis of~$\R^{Q_0}$.
